\documentclass{sig-alternate}

\pdfpagewidth=8.5in 
\pdfpageheight=11in 

\usepackage{breqn}
\usepackage{pbox}
\usepackage{enumitem, array}
\usepackage{hyperref}
\usepackage{times}
\usepackage{balance}
\usepackage{xspace}
\usepackage{url}
\usepackage{cite}
\usepackage{balance}

\setlist{nolistsep}
\setlength{\textfloatsep}{10pt}


\usepackage{listings}
\lstset{
  breaklines=true,
}

% Markup macros for proof-reading
\usepackage[normalem]{ulem} % for \sout
\usepackage{xcolor}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\ugh}[1]{\textcolor{red}{\uwave{#1}}} % please rephrase
\newcommand{\ins}[1]{\textcolor{blue}{\uline{#1}}} % please insert
\newcommand{\del}[1]{\textcolor{red}{\sout{#1}}} % please delete
\newcommand{\chg}[2]{\textcolor{red}{\sout{#1}}{\ra}\textcolor{blue}{\uline{#2}}} % please change

% Put edit comments in a really ugly standout display
\usepackage{ifthen}
\usepackage{amssymb}
\newboolean{showcomments}
\setboolean{showcomments}{false} % toggle to show or hide comments
\ifthenelse{\boolean{showcomments}}
  {\newcommand{\nb}[2]{
    \fcolorbox{gray}{yellow}{\bfseries\sffamily\scriptsize#1}
    {\sf\small$\blacktriangleright$\textit{#2}$\blacktriangleleft$}
   }
   \newcommand{\version}{\emph{\scriptsize$-$working$-$}}
  }
  {\newcommand{\nb}[2]{}
   \newcommand{\version}{}
  }

\newcommand\gs[1]{\nb{Georgios}{#1}}
\newcommand\bv[1]{\nb{Bogdan}{#1}}
\newcommand\as[1]{\nb{Alexander}{#1}}


\newcommand{\inlinecode}[1] {\lstinline[basicstyle=\ttfamily]{#1}}
\newcommand{\f}[2]{\text{\textit{#1}}\mbox{#2}}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}

\def\sharedaffiliation{\end{tabular}\newline\begin{tabular}{c}}


\newcommand{\ght}{\textsc{GHT}orrent\xspace}
\newcommand{\api}{\textsc{api}\xspace}
\newcommand{\gh}{\textsc{GitHub}\xspace}
\newcommand{\ohloh}{\textsc{Ohloh}\xspace}
\newcommand{\flossmole}{\textsc{FLOSSmole}\xspace}


\def\tud{\textsuperscript{*}}
\def\tue{\textsuperscript{\dag}}

\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}


\widowpenalty=30000
\clubpenalty=30000


\begin{document}

% --- Author Metadata here ---
\conferenceinfo{MSR}{'14, May 31 -- June 1, 2014, Hyderabad, India}
\CopyrightYear{2014}
\crdata{978-1-4503-2863-0/14/05}
% --- End of Author Metadata ---

\title{Lean GHTorrent: GitHub Data on Demand}


\numberofauthors{1}

\author{
Georgios Gousios\tud, Bogdan Vasilescu\tue, Alexander Serebrenik\tue, Andy Zaidman\tud\\
\sharedaffiliation
  \begin{tabular}{ccc}
    \affaddr{\tud Delft University of Technology} && \affaddr{\tue Eindhoven University of Technology}\\
   \affaddr{Delft, The Netherlands} && \affaddr{Eindhoven, The Netherlands}\\
   \email{\{g.gousios, a.e.zaidman\}@tudelft.nl} && \email{\{b.n.vasilescu, a.serebrenik\}@tue.nl} \\
  \end{tabular}
}


\maketitle
\begin{abstract}

In recent years, \gh has become the largest code host in the world, with more than 5M developers
collaborating across 10M repositories.
Numerous popular open source projects (such as Ruby on Rails, Homebrew, Bootstrap, Django or jQuery)
have chosen \gh as their host and have migrated their code base to it.
\gh offers a tremendous research potential.
For instance, it is a flagship for current open source development, a place for developers to showcase
their expertise to peers or potential recruiters, and the platform where social coding features or
pull requests emerged.
However, \gh data is, to date, largely underexplored.
To facilitate studies of \gh, we have created \ght, a scalable, queriable, offline mirror of the data offered
through the \gh REST API.
In this paper we present a novel feature of \ght designed to offer customisable data dumps on demand.
The new \ght data-on-demand service offers users the possibility to request via a web form
up-to-date \ght data dumps for any collection of \gh repositories.
We hope that by offering customisable \ght data dumps we will not only lower the ``barrier for entry''
even further for researchers interested in mining \gh data (thus encourage researchers to intensify their
mining efforts), but also enhance the replicability of \gh studies (since a snapshot of the data on which
the results were obtained can now easily accompany each study).
%The service is available at \url{http://ghtorrent.org/lean}.
\end{abstract}


\category{H.3.5}{Online Information Services}{Data sharing}. 
\terms{Experimentation}
\keywords{GitHub, dataset, data on demand}



\input{introduction}

\input{architecture}

\input{usage}

\input{limitations}

\input{relwork}

\input{conclusions}

\input{acknowledgements}

\balance

{\small
\bibliographystyle{abbrv}
\bibliography{ref}
}

\end{document}
